Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-02-25 doc/paper.Rmd
error rate reporting modified from absolute numbers to rates

Digitized images, e.g. profilometers or confocal microscopy allow us to measure the surface \citep{vorburger2016} and can be used to conduct statistical analysis on the markings. Multiple toolmarks have been studied in the literature:  \citet{manytoolmarks1, chumbley} have studied screwdriver marks digitized using a profilometer,  \citet{manytoolmarks2} have investigated screwdriver, tongue and groove pliers marks that are generated using a confocal microscope,  while slip-joint pliers have been investigated by \citet{afte-chumbley} using digitized marks generated by a surface profilemeter. \citet{manytoolmarks1} used an algorithm which compares many small windows in the markings between two toolmarks and the maximum pearson correlation coefficient as the statistical index for concluding matches and non-matches. The Chumbley scoring method, first introduced by \citet{chumbley} uses a similar but much more extenstive framework which includes a non-parametric statistical test. This was later improved by Hadler and Morris \citep{hadler}. In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assessing striation marks on bullets for same-source identification.

@@

Bullet matching methods depend on the attribute being used for making comparisons. For single feature based matching \citet{chu2013} used an automatic method for counting consequtive matching striae (CMS). They reported zero false positive rate but do not discuss about the false negative rates for land to land matches. \citet{ma2004} and \citet{vorburger2011} discuss about CCF (cross-correlation function) and its discriminating power and application but do not talk about matches and non-matches. \citet{aoas} use multiple attributes like CCF, CMS and compare every land against every other land of the Hamby dataset \citet{hamby}. This also includes matching of all the unknown bullet lands against the known bullet lands. They report for 10,731 comparisons, 18 false negatives and 9 false negatives.

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks.
\citet{chumbley}, in their paper, compare two toolmarks with the intention of determining if it comes from the same tool. The data for their study was obtained from 50 sequentially manufactured screwdriver tips. For every 100 comparisons \citet{chumbley} reported 2 false negatives and 9 false positives. The improvement proposed by \citet{hadler} on the other hand gave 0 false  negatives and 3 false poisitives.

@@

```{r, results='asis'}
library(knitr)
library(kableExtra)
library(xtable)

a1<- matrix(NA, ncol = 3, nrow = 2)
toolmark1.confusion<- data.frame(a1)
colnames(toolmark1.confusion)<- c("Classification", "Match", "Non-Match")
toolmark1.confusion$Classification<- c("Match", "Non-Match")
toolmark1.confusion$Match<- c(41,2)
toolmark1.confusion$`Non-Match`<- c(9,48)

>>>>

Digitized images, e.g. profilometers or confocal microscopy allow us to measure the surface \citep{vorburger2016} and can be used to conduct statistical analysis on the markings. Multiple toolmarks have been studied in the literature:  \citet{manytoolmarks1, chumbley} have studied screwdriver marks digitized using a profilometer,  \citet{manytoolmarks2} have investigated screwdriver, tongue and groove pliers 3D marks that are generated using a confocal microscope,  while, slip-joint pliers have been investigated by \citet{afte-chumbley} using digitized marks generated by a surface profilemeter. \citet{manytoolmarks2} define a relative distance metric and use it as similarity measure between two toolmarks. \citet{manytoolmarks1} used an algorithm which compares many small segments in the markings between two toolmarks. A maximum pearson correlation coefficient is then used as the statistical index for comparison. The Chumbley scoring method, first introduced by \citet{chumbley}, uses a similar but much more extenstive framework which includes a non-parametric statistical test. This was later improved by Hadler and Morris \citep{hadler}. In this paper, we are investigating the applicability of the Chumbley scoring method by \citet{hadler} to assessing striation marks on bullets for same-source identification.

@@

Bullet matching methods depend on the attribute being used for making comparisons. For single feature based matching \citet{chu2013} used an automatic method for counting consequtive matching striae (CMS). They reported zero false positive rate but do not discuss about the false negative rates for land to land matches. \citet{ma2004} and \citet{vorburger2011} discuss about CCF (cross-correlation function) and its discriminating power and application but do not talk about matches and non-matches. \citet{aoas} use multiple attributes like CCF, CMS, D (distance measure) etc in a random forrest based method and compare every land against every other land of the Hamby dataset \citet{hamby}. They report an out-of-bag error rate with  false positive error rate of 0.0001 and false negative error rate of 0.2267 for 100 trees. For 300 trees they report correct prediction of all matches and non-matches.

The Chumbley score  provides us with another approach in the same-source assessment of bullet striation marks.
\citet{chumbley}, in their paper, compare two toolmarks with the intention of determining if it comes from the same tool. The data for their study was obtained from 50 sequentially manufactured screwdriver tips.\citet{chumbley} reported error rates for marking made by the tips at differnt angles. For a 30 degree they showed false negative error rate to be 0.023 and  false positive error rate be 0.09. For other angles the error rates remain the same for false negatives and 0.01 for false positives. The improvement proposed by \citet{hadler} on the other hand, did not consider effect of angles and gave 0.06 false  negative error rate and 0 false poisitive error rate for markings made at the same angle.

@@

```{r, results='asis', include=FALSE}
library(knitr)
library(kableExtra)
library(xtable)

a1<- matrix(NA, ncol = 3, nrow = 2)
toolmark1.confusion<- data.frame(a1)
colnames(toolmark1.confusion)<- c("Classification", "Match", "Non-Match")
toolmark1.confusion$Classification<- c("Match", "Non-Match")
# toolmark1.confusion$Match<- c(41,2)
# toolmark1.confusion$`Non-Match`<- c(9,48)
toolmark1.confusion$Match<- c(91,2)
toolmark1.confusion$`Non-Match`<- c(9,98)
